Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-10-25 Ch1_movement_rates/Ch1_Figures.Rmd
Figure 2 is ready

```{r fig.height=12}
# Visualize distribution and data points

@@

indiv_moverate %>%
  ggplot(., aes(x = movrate, y = 0.002, color = fam_g)) +
  geom_point(size = 3, alpha = 0.8) +
  # geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
                color = "black", alpha = 0.8, size = 1) +
  scale_color_manual(values = cols.fig2) +
  labs(x = "Movement Rate (meters/minute)", y = "Density",
       title = "Lognormal fit to individual movement rates") +
  #geom_vline(xintercept = vlines, color = my.cols1[4], size = 1, lty = 2) +
  scale_x_continuous(limits = c(0, 70)) +
  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
  guides(color = guide_legend(title = "Social Group",
                              ncol = 2)) +
  theme_bw() +
  theme(legend.position = c(0.8, 0.6)) -> logfit_plot

@@

plot_grid(logfit_plot, social_group_curves, nrow = 2)

# ggsave2(filename = "Ch1_movement_rates/Figures/Figure2.png")

@@

```{r include=FALSE}
# The average movement rate for this sample of the population (the 12 individuals) is the average of the movement rate for each individual:

# mean(indiv_moverate$movrate)
# 27.94211 meters/minute

# In a complete pooling approach, we take this average movement rate and use it as the parameter for our exponential distribution, from which we draw the movement distance at each time step.

## Compare exponential movement distances to full dataset ----------------------------------

movrate_cp <- mean(indiv_moverate$movrate)
movrate_cp_ln <- as.numeric(exp(logfit$estimate[1]))

# test <- data.frame(mpm = rexp(500, rate = 1/movrate_cp))
#
# test %>%
#   ggplot(., aes(x = mpm)) +
#   geom_histogram(aes(y = ..density..)) +
#   stat_function(fun = dexp, args = list(rate = 1/movrate_cp), color = "red")

ptpl %>%
  ggplot(., aes(x = mpm)) +
  geom_histogram(aes(y = ..density..)) +
  stat_function(fun = dexp, args = list(rate = 1/movrate_cp), color = my.cols1[4], size = 1) +
  stat_function(fun = dexp, args = list(rate = 1/movrate_cp_ln), color = my.cols1[3], size = 1, alpha = 0.8) +
  labs(title = "Histogram of movement distances per minute from data set",
       x = "Movement distance per minute",
       y = "Density",
       caption = "Orange line is exponential density using average movement rate for population \n
       Yellow line shows exponential density using mean estimate from lognormal fit to movement rates") +
  theme_bw()

@@

```{r include=FALSE}
## Visualize mov rates ---------------
pp_1 <- sort(round(fam_moverate$movrate,3))

### Compare lognorm fits CP and PP -----------

logfit_fam <- fitdist(pp_1, distr = 'lnorm')
# normfit <- fitdist(indiv_moverate$movrate, distr = "norm")

# Mean using the fit
# exp(logfit_fam$estimate[1])

```{r}
# Visualize distribution and data points
vlines_fam <- summary(fam_moverate$movrate)[c(1,3,6)]

indiv_moverate %>%
  ggplot(., aes(x = movrate, y = 0.002)) +
  # stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
  #               color = "black", alpha = 0.8, size = 1) +
  # geom_point(size = 3, alpha = 0.8) +
  # geom_vline(xintercept = vlines, color = "black", size = 1, lty = 2) +
  # scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60),
  #                    labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),
                color = my.cols1[4], alpha = 0.8, size = 1) +
  geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
  geom_vline(xintercept = vlines_fam, color = my.cols1[4], size = 1, lty = 2) +
  scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines_fam[1], 20, vlines_fam[2], vlines_fam[3], 60),
                     labels = c(0, "Min.", 20, "Median.", "Max.", 60)) +
  labs(x = "Movement Rate (meters/minute)", y = "Density",
       title = "Lognormal fit to family group movement rates") +
  theme_bw()

# ggsave2(filename = "Ch1_movement_rates/Figures/logfit_pp.png")

```{r include=FALSE}
## Visualize mov rates ---------------
pp_1 <- sort(round(fam_moverate$movrate,3))

### Compare lognorm fits CP and PP -----------

logfit_fam <- fitdist(fam_moverate$movrate, distr = 'lnorm')
# normfit <- fitdist(indiv_moverate$movrate, distr = "norm")

# Mean using the fit
exp(logfit_fam$estimate[1])

```{r}
# Visualize distribution and data points
vlines_fam <- summary(fam_moverate$movrate)[c(1,3,6)]

indiv_moverate %>%
  ggplot(., aes(x = movrate, y = 0.002)) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
                color = "black", alpha = 0.8, size = 1) +
  geom_point(size = 3, alpha = 0.8) +
  geom_vline(xintercept = vlines, color = "black", size = 1, lty = 2) +
  scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60),
                     labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) +
  # stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),
  #               color = my.cols1[4], alpha = 0.8, size = 1) +
  geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
  # geom_vline(xintercept = vlines_fam, color = my.cols1[4], size = 1, lty = 2) +
  labs(x = "Movement Rate (meters/minute)",
       # title = "Average movement rates lognormal fits",
       y = "Density") +
  theme_bw()
```

```{r}
## PP w/fam moverates ---------------------------------------
# Meaning, we use the average movement rate for each family group as the parameter for an exponential from which we draw movement distances for the simulation.

fam_moverate %>%
  arrange(., movrate) -> fam_moverate

fam_moverate %>%
  ggplot(., aes(x = movrate, y = 0, color = movrate)) +
  geom_point(size = 3) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),
                color = my.cols1[4], alpha = 0.8, size = 1) +
  xlim(0, 60) +
  labs(title = "Lognormal fitted to family group",
       x = "Movement rate",
       y = "Density") +
  scale_color_viridis_c() +
  theme_bw() +
  theme(legend.position = "none") -> pp_logfit

mycols2 <- viridisLite::viridis(7)
expcurves_pp1 <- purrr::map(seq(1:7), function(y)
  stat_function(fun = dexp, args = list(rate = 1/fam_moverate$movrate[y]), color = mycols2[y], alpha = 0.8))

ggplot() +
  expcurves_pp1 +
  xlim(-1, 125) +
  labs(title = "Movement distance exponential draws", x = 'Movement Distance', y = "Density") +
  theme_bw() -> pp_expdraws

cowplot::plot_grid(pp_logfit, pp_expdraws)
# ggsave2(filename = "Ch1_movement_rates/Figures/pp_logfit_plus_exp.png")
```

```{r include=FALSE}
# This one looks at individual variation.
# We will sample 20 individuals, 3 times from the lognormal distribution that describes movement rates for the population
logfit <- fitdist(indiv_moverate$movrate, distr = 'lnorm')

n.individuals <- 20
m_1 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3))
m_2 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3))
m_3 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3))

logfitdraw <- data.frame(indv = 1:20, m_1 = m_1, m_2 = m_2, m_3 = m_3)

indiv_moverate %>%
  ggplot(., aes(x = movrate, y = 0)) +
  geom_point(size = 5) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]), color = "black", alpha = 0.8) +
  geom_point(data = logfitdraw, aes(x = m_1, color = factor(indv), y = 0.005), size = 3) +
  geom_point(data = logfitdraw, aes(x = m_2, color = factor(indv), y = 0.006), size = 3) +
  geom_point(data = logfitdraw, aes(x = m_3, color = factor(indv), y = 0.007), size = 3) +
  # scale_color_viridis_d(option="magma") +
  scale_color_viridis_d() +
  xlim(0, 60) +
  labs(title = "Sampling individuals from lognormal",
       x = "Movement rate",
       y = "Density") +
  theme_bw() +
  theme(legend.position = "none") -> plot.logfitdraw

plot.logfitdraw

mycols <- viridisLite::viridis(20)

expcurves_m1 <- purrr::map(seq(1:n.individuals), function(y)
  stat_function(fun = dexp, args = list(rate = 1/logfitdraw$m_1[y]), color = mycols[y], alpha = 0.8))

expcurves_m2 <- purrr::map(seq(1:n.individuals), function(y)
  stat_function(fun = dexp, args = list(rate = 1/logfitdraw$m_2[y]), color = mycols[y], alpha = 0.8))

expcurves_m3 <- purrr::map(seq(1:n.individuals), function(y)
  stat_function(fun = dexp, args = list(rate = 1/logfitdraw$m_3[y]), color = mycols[y], alpha = 0.8))

logfitdraw %>%
  ggplot() +
  expcurves_m1 +
  expcurves_m2 +
  expcurves_m3 +
  xlim(-1, 125) +
  labs(title = "Movement distance Exponential Draws", x = 'Movement Distance', y = "Density") +
  theme_bw() -> expdraws
expdraws

cowplot::plot_grid(plot.logfitdraw, expdraws)

# ggsave2(filename = "Ch1_movement_rates/Figures/Sampling_indivs_lnorm.png")
```

In process

>>>>

```{r}
# Visualize distribution and data points

@@

# Movement rates used for each scenario

movrate_cp
movrate_np
movrate_pp

movratedf <- data.frame(scenario = "cp", group = NA, movrate = movrate_cp) %>% 
  bind_rows(., data.frame(scenario = rep("pp", 42), group = movrate_pp$fam_g, movrate = movrate_pp$movrate)) %>% 
  bind_rows(., data.frame(scenario = rep("np", 30), group = NA, movrate = movrate_np))

# Logfit plot

indiv_moverate %>%
  ggplot(., aes(x = movrate, y = 0.002, color = fam_g)) +
  geom_point(size = 3, alpha = 0.8) +
  # geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
                color = "black", alpha = 0.8, size = 1) +
  scale_color_manual(values = cols.fig2) +
  labs(x = "Movement Rate (meters/minute)", y = "Density",
       title = "Lognormal fit to individual movement rates") +
  #geom_vline(xintercept = vlines, color = my.cols1[4], size = 1, lty = 2) +
  scale_x_continuous(limits = c(0, 70)) +
  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
  guides(color = guide_legend(title = "Social Group",
                              ncol = 2)) +
  theme_bw() +
  theme(legend.position = "none") -> logfit_plot

@@

movratedf %>% 
  ggplot(., aes(x = movrate, y = factor(scenario, levels = c("pp", "np", "cp")), color = as.character(group))) +
  geom_point(size = 3, alpha = 0.8) +
  scale_color_manual(values = cols.fig2) +
  scale_x_continuous(limits = c(0, 70)) +
  labs(x = "Movement Rate (meters/minute)", y = "Model scenario",
       title = "Sampled movement rates for each simulated scenario") +
  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
  guides(color = guide_legend(title = "Social Group",
                              ncol = 2)) +
  theme_bw() +
  theme(legend.position = "none") -> movrates_used

@@

```{r fig.height=12}
plot_grid(logfit_plot, social_group_curves, movrates_used, nrow = 3, rel_heights = c(2,2,1))

ggsave2(filename = "Ch1_movement_rates/Figures/Figure2.png")

@@
